Deviance in a generalized linear model

### 2021-10-23 text/20/ihme-model.Rmd
Relocated .Rmd files

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: "New"
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

>>>>

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: "New"
date: 2020-04-23
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

### 2021-10-23 text/20/non-breaking-spaces.Rmd
Relocated .Rmd files

---
title: "Blog post: Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: "New"
date: "2020-01-07"
categories:
- Blog post
tags:
- Data management
output: html_document
---

>>>>

---
title: "Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: "New"
date: "2020-01-07"
categories:
- Blog post
tags:
- Data management
output: html_document
---

### 2021-10-23 text/20/poisson-inferences.Rmd
Relocated .Rmd files

---
title: "Working with the Poisson distribution"
author: "Steve Simon"
source: "New"
date: "2020-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

>>>>

---
title: "Working with the Poisson distribution"
author: "Steve Simon"
source: "New"
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

### 2021-10-23 text/20/reading-text-files.Rmd
Relocated .Rmd files

![A non-text file displayed in notepad](../../../web/images/reading-text-files01.png)

@@

![Data set on movies](../../../web/images/read-text-files03.png)

@@

![Data dictionary](../../../web/images/read-text-files06.png)

@@

![Example of a space delimited file](../../../web/images/read-text-files02.png)

@@

![Dataset showing COVID-19 deaths over time](../../../web/images/read-text-files04.png)

@@

![Dataset of revenues for selected movies](../../../web/images/read-text-files05.png)

>>>>

```{}
![A non-text file displayed in notepad](../../../web/images/reading-text-files01.png)
```

@@

```{}
![Data set on movies](../../../web/images/read-text-files03.png)
```

@@

```{}
![Data dictionary](../../../web/images/read-text-files06.png)
```

@@

```{}
![Example of a space delimited file](../../../web/images/read-text-files02.png)
```

@@

```{}
![Dataset showing COVID-19 deaths over time](../../../web/images/read-text-files04.png)
```

@@

```{}
![Dataset of revenues for selected movies](../../../web/images/read-text-files05.png)
```

### 2021-10-23 text/21/anonymizing-ids.Rmd
Relocated .Rmd files

---
title: "Anonymizing ids"
author: "Steve Simon"
source: "New"
date: "2020-06-10"
categories:
- Blog post
tags:
- Privacy in research
output: html_document
---

>>>>

---
title: "Anonymizing ids"
author: "Steve Simon"
source: "New"
date: "2021-06-10"
categories:
- Blog post
tags:
- Privacy in research
output: html_document
---

### 2021-10-23 text/21/glm-deviance.Rmd
Relocated .Rmd files

---
title: "Deviance in a generalized linear model"
author: "Steve Simon"
source: "New"
date: "2020-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Deviance in a generalized linear model"
author: "Steve Simon"
source: "New"
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---
